An ICM Paper Made by Team 0000111

### 2020-01-12 easymcm/PAPER.tex
基本定稿

For task 1, we first distinguished the concepts of urban, suburban, and rural area according to the population density in the United State. Based on the queuing theory and the data we get by linear and quadratic fitting, we found that the average waiting time for each charging station is 5.32 hours which indicates that Tesla cannot meet the goal of all-electric vehicles in the future. Next, we established a two-objective programming model, it turned out that the required number of charging stations is 16,025 with the base ratio 3.23: 1.07: 0.34\ (urban, suburban and rural areas).

In the part of task 2, we choose South Korea as the reserch object. We established a station quantity model and a station position model to analyze the distribution of charging stations between regions. Through relationship between the vehicle power consumption and the charging capacity provided by the charging stations we estimated the total number of charging staion in South Korea. In the station position model, after comprehensively considering the traffic flow of each location on the highway and the distance between each node, we established a two-objective planning model under the conditions of the shortest distance and the maximum flow for station position.

>>>>

For task 1, we first distinguished the concepts of urban, suburban, and rural area according to the population density in the US. Based on the queuing theory and the data we get by linear and quadratic fitting, we found that the average waiting time for each charging station is 5.32 hours which indicates that Tesla cannot meet the goal of all-electric vehicles in the future. Next, we established a two-objective programming model, it turned out that the required number of charging stations is 16,025 with the base ratio 3.23: 1.07: 0.34\ (urban, suburban and rural areas).

In the part of task 2, we choose South Korea as the reserch object. We established a station quantity model and a station position model to analyze the distribution of charging stations between regions. Through relationship between the vehicle power consumption and the charging capacity provided by the charging stations we estimated the total number of charging staion in South Korea. In the station position model, after comprehensively considering the traffic flow of each location on the highway and the distance between each node, we established a two-objective programming model under the conditions of the shortest distance and the maximum flow for station position.
